Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-03-30 supplement.tex
Added simplified version of pirouette example 30 code

\begin{itemize}
  \item{
    subsection \ref{subsec:guidelines}: guidelines for empiricists
  }
  \item{
    subsection \ref{subsec:installation}: installation
  }
  \item{
    subsection \ref{subsec:resources}: resources, such as 
    website, tutorials, packages used, bug reporting and contributing
  }
  \item{
    subsection \ref{subsec:citation}: citation of pirouette
  }
  \item{
    subsection \ref{subsec:main_functions}: main functions
  }
  \item{
    subsection \ref{subsec:main_example}: extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
%  \item{
%    subsection \ref{subsec:non_clock}: the %effect when the alignment
%    is generated by a non-clock like nucleotide substitution model
%  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:different_n_mutations} shows the
    effect when the twin alignment is allowed to have a different
    number of mutations
  }
  \item{
    subsection \ref{subsec:mutation_rate} shows the
    effect of different mutation rates
  }
\end{itemize}

@@

The code to reproduce this can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_30}.

>>>>

\begin{itemize}
  \item{
    subsection \ref{subsec:guidelines}: guidelines for empiricists
  }
  \item{
    subsection \ref{subsec:installation}: installation
  }
  \item{
    subsection \ref{subsec:resources}: resources, such as 
    website, tutorials, packages used, bug reporting and contributing
  }
  \item{
    subsection \ref{subsec:citation}: citation of pirouette
  }
  \item{
    subsection \ref{subsec:main_functions}: main functions
  }
  \item{
    subsection \ref{subsec:main_example}: code, extra figures and
    diagnostics regarding the main example.
  }
  \item{
    subsection \ref{subsec:distribution}: the result of using 
    multiple trees, as generated by the
    same stochastic process as the main example
  }
  \item{
    subsection \ref{subsec:n_taxa}: the effect of the number
    of taxa
  }
  \item{
    subsection \ref{subsec:n_nucleotides}: the effect of the DNA
    alignment sequence length
  }
%  \item{
%    subsection \ref{subsec:non_clock}: the %effect when the alignment
%    is generated by a non-clock like nucleotide substitution model
%  }
  \item{
    subsection \ref{subsec:simplest_correct_parameterization} shows the
    effect when doing an inference in the simplest use case
  }
  \item{
    subsection \ref{subsec:under_parameterization} shows the
    effect when doing an inference with an under-parameterization
  }
  \item{
    subsection \ref{subsec:different_n_mutations} shows the
    effect when the twin alignment is allowed to have a different
    number of mutations
  }
  \item{
    subsection \ref{subsec:mutation_rate} shows the
    effect of different mutation rates
  }
\end{itemize}

@@

The code to reproduce this can be found at  
\url{https://github.com/richelbilderbeek/pirouette_example_30}
and a simplified version is shown for convenience here as well:

\begin{lstlisting}[language=R]
library(pirouette)

# Create phylogeny
set.seed(314)
phylogeny <- create_exemplary_dd_tree(
  n_taxa = 6, 
  crown_age = 10
)

# Setup pirouette
pir_params <- create_std_pir_params(
  folder_name = "example_30"
)

# Do the runs
pir_out <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)

# Save
library(ggplot2)
pir_outs <- list()
pir_outs[[1]] <- pir_out
pir_plots(pir_outs) +
  ggtitle("pirouette example 30") +
  ggsave("errors.png", width = 7, height = 7)

pir_save(
  phylogeny = phylogeny,
  pir_params = pir_params,
  pir_out = pir_out,
  folder_name = "example_30"
)
\end{lstlisting}
